Evolution, functional diversity, regime shifts, hysteresis, and nonlinearity; ecosystem responses to environmental change.

### 2021-06-23 manuscript/article.Rmd
new var pars

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
result_index2 <- 2
p2  <- plot_ss_result1(CBSBPB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

>>>>

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
result_index2 <- 20
p2  <- plot_ss_result1(CBSBPB_data,
                result_index = result_index2,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2
